基于卷积神经网络的视觉目标跟踪算法研究

### 2021-03-02 博士/毕业论文/ucasthesis/Tex/Backmatter.tex
增加在投文章

\section*{已发表(或正式接受)的学术论文:}

{
\setlist[enumerate]{}% restore default behavior
\begin{enumerate}[nosep]
    \item \textbf{Zhenbang Li}, Qiang Wang, Jin Gao,  Bing Li, Weiming Hu, "Globally Spatial-Temporal Perception: A Long-Term Tracking System", \textit{International Conference on Image Processing} (\textbf{ICIP}), 2020. (CCF C类)
    \item \textbf{Zhenbang Li}, Qiang Wang, Jin Gao,  Bing Li, Weiming Hu, "End-to-End Temporal Feature Aggregation For Siamese Trackers", \textit{International Conference on Image Processing} (\textbf{ICIP}), 2020. (CCF C类)
    \item \textbf{Zhenbang Li}, Bing Li, Jin Gao, Liang Li, Weiming Hu, "Manipulating Template Pixels for Model Adaptation of Siamese Visual Tracking", \textit{IEEE Signal Processing Letters}, 2020.
\end{enumerate}
}

>>>>

\section*{已发表（或正式接受）的学术论文:}

{
\setlist[enumerate]{}% restore default behavior
\begin{enumerate}[nosep]
    \item \textbf{Zhenbang Li}, Qiang Wang, Jin Gao,  Bing Li, Weiming Hu, "Globally Spatial-Temporal Perception: A Long-Term Tracking System", \textit{International Conference on Image Processing} (\textbf{ICIP}), 2020.
    \item \textbf{Zhenbang Li}, Qiang Wang, Jin Gao,  Bing Li, Weiming Hu, "End-to-End Temporal Feature Aggregation For Siamese Trackers", \textit{International Conference on Image Processing} (\textbf{ICIP}), 2020.
    \item \textbf{Zhenbang Li}, Bing Li, Jin Gao, Liang Li, Weiming Hu, "Manipulating Template Pixels for Model Adaptation of Siamese Visual Tracking", \textit{IEEE Signal Processing Letters}, 2020.
\end{enumerate}
}

\section*{已投稿的学术论文:}

{
\setlist[enumerate]{}% restore default behavior
\begin{enumerate}[nosep]
    \item \textbf{Zhenbang Li}, Jin Gao, Yaya Shi, Bing Li, Pengpeng Liang, Weiming Hu, "Video-Agnostic Perturbations: Efficient Targeted Attacks for Siamese Visual Tracking", \textit{International Joint Conference on Artificial Intelligence} (\textbf{IJCAI}), 2021.
    \item Yaya Shi, Chunfeng Yuan, \textbf{Zhenbang Li}, Ziqi Zhang, Bing Li, Zheng-Jun Zha, Weiming Hu, "VTMScore: Evaluating Video Captioning via Video-Text Matching", \textit{Proceedings of the 50th Annual Meeting of the Association for Computational Linguistics} (\textbf{ACL}), 2021.
\end{enumerate}
}
